### 2020-07-25 ChapterProblemDefinition/chapterProblemDefinition.tex
Updated: What is the limit and added benefits of scalability of your approach

>>>>

\section{Benefits of Proposed Solution}
Aura Projection has the following benefits over other considered solutions. AP guarantees strong consistency of collisions, meaning diverging results on different servers are prevented. Objects are only simulated once on a one server, instead of being simulated on multiple servers, requiring more computation time per object. No synchronisation is required between servers, as each server is running an entirely autonomous simulation, there is no need for any synchronisation to take place between servers.

\section{Limits of Proposed Solution}
Performance of the system will be measured using the highest cost across all servers, this will be referred to as $costmax$. If the addition of one or more servers (and/or re-partitioning of servers) cannot be done without causing a higher $costmax$, the system cannot be scaled up further.

It is possible to predict whether or not a new configuration has a higher or lower $costmax$ using the following process. Let B:N be the performance cost ratio of boundary to non-boundary objects (this cost ratio will differ for different simulations and may either be a constant ratio or a function, but we will assume it is a constant for this estimate). Due to boundary objects having additional processing and networking overhead, we can assume the B:N ratio will always be greater than 1. The performance cost can then be estimated for each server in the new configuration by summing the boundary and non-boundary objects and using the B:N cost estimate. If this results in a lower $costmax$ the performance of the system will be increased.

Let $cost(x)$ be the performance cost of a server x.
Let $Obj_{bdry}$ and $Obj_{nonbdry}$ be the number of boundary and non-boundary objects respectively for a given server x.

\begin{equation}
	cost(x) = (Obj_{bdry}\cdot B:N) + Obj_{nonbdry}
\end{equation}

Let N be the number of servers. The $cost_max$ of a server can be calculated using the following equation:
\begin{equation}
	costmax = max(cost(1),...,cost(N))
\end{equation}

Let $costmax_n$ be the current $costmax$ of system and $costmax_{n+1}$ be the $costmax$ of a potential new configuration.

\begin{equation}
	costmax_{n+1} < costmax_n
\end{equation}

The $costmax_{n+1}$ must be less than $costmax_n$ in order for a performance gain to occur. If no possible $costmax_{n+1}$ with a lower value exists, the overall performance of the system cannot be increased and the system will have reached the limit of scalability.

Example 1:
Let 1 non-boundary object have the cost value of 1 and suppose the B:N ratio is a constant 2:1.
1 server with 1000 non-boundary objects. The $costmax_n$ is 1000. 1 server is added, the simulation is partitioned so that 500 non-boundary objects exist on each. The $costmax_{n+1}$ is 500. 500<1000, so new configuration results in better performance.

Example 2:
2 servers with 1000 non-boundary objects each. The $costmax_n$ is 1000. 1 server is added, the simulation, the best partitioning that can be achieved results in 1 server having 250 non-boundary and 400 boundary objects. The $costmax_{n+1}$ is (400*B:N)+250 = 1050. 1050>1000, so the new configuration results in worse performance. As this is the best partitioning that could be achieved the system cannot be scaled up further.

Using the logic above and the assumptions made, it can be deduced that the main limiting factor of Aura Projection is the number of unavoidable boundary objects present on a single server in the simulation.
